---
title: "Exercise 2"
---

Enhance your application with pre-built modules!

Reference:

- [`teal.modules.general::tm_data_table()`](https://insightsengineering.github.io/teal.modules.general/latest-tag/reference/tm_data_table.html) to create a data previewer module
- [`teal.modules.clinical::tm_t_summary()`](https://insightsengineering.github.io/teal.modules.clinical/latest-tag/reference/tm_t_summary.html) to create a demographic summary table:
  - please read the documentation - especially `arm_var` and `summarize_vars` argument and what data type it takes
  - use both `"ARM"` and `"ARMCD"` as `arm_var`
  - use `"SEX"`, `"AGE"` and `"RACE"` as `summarize_vars`

### Example

```{r ex, message = FALSE}
library(dplyr)
library(teal.modules.general)
library(teal.modules.clinical)

# Prepare data object
data <- teal_data()
data <- within(data, {
  ADSL <- rADSL
})
join_keys(data) <- default_cdisc_join_keys["ADSL"]


# Prepare module inputs
ADSL <- data[["ADSL"]]

cs_arm_var <- choices_selected(
  choices = variable_choices(ADSL, subset = c("ARMCD", "ARM")),
  selected = "ARM"
)

demog_vars_adsl <- ADSL |>
  select(where(is.numeric) | where(is.factor)) |>
  names()


# Create app
app <- init(
  data = data,
  modules = list(
    tm_data_table("Data Table"),
    tm_t_summary(
      label = "Demographic Table",
      dataname = "ADSL",
      arm_var = cs_arm_var,
      summarize_vars = choices_selected(
        choices = variable_choices(ADSL, demog_vars_adsl),
        selected = c("SEX", "AGE", "RACE")
      )
    )
  )
)

if (Sys.getenv("QUARTO_ROOT") == "") {
  shinyApp(app$ui, app$server)
}
```

```{r save_script, include = FALSE}
code <- paste0(knitr::knit_code$get("ex"), collapse = "\n")
writeLines(code, "scripts/exercise_2.R")
```

```{r parse_shinylive_url, include = FALSE}
url <- roxy.shinylive::create_shinylive_url(code)
url_editor <- roxy.shinylive::create_shinylive_url(code, mode = "editor")
```

### App

```{r shinylive_iframe, echo = FALSE, out.width = '150%', out.extra = 'style = "position: relative; z-index:1"', purl = FALSE}
knitr::include_url(url, height = "800px")
```

### Exercise

```{r shinylive_link, echo = FALSE, results = 'asis', purl = FALSE}
cat(sprintf("[Open editor in Shinylive](%s)\n\n", url_editor))
```

The module output requires further tweaks:

- We dont' want to have "ALL PATIENT" column - let's remove it. Please read function documentation and identify the argument to be changed.

  ::: {.callout-tip collapse="true"}
  ## Answer

  ```{r, eval = FALSE}
  tm_t_summary(
    ...,
    add_total = FALSE
  )
  ```
  :::

- It is possible to select "ARM" in the "Summarize Variables" input which does not make much sense. Let's limit the selection to only a few interesting columns of your choice. Which object to change?

  ::: {.callout-tip collapse="true"}
  ## Answer

  ```{r, eval = FALSE}
  # explicit
  demog_vars_adsl <- c("AGE", "SEX", "RACE", ...)
  # alternatively: exclude
  demog_vars_adsl <- ... |> setdiff(c("AGE", ...))
  ```
  :::

- Let's create two modules in the same application - one with "ARM" column as `arm_var` and the other with "ARMCD".

  ::: {.callout-tip collapse="true"}
  ## Answer

  ```{r, eval = FALSE}
  app <- init(
    ...
    modules = list(
      ...,
      tm_t_summary(
        ...,
        arm_var = choices_selected("ARM", "ARM", fixed = TRUE)
      ),
      tm_t_summary(
        ...,
        arm_var = choices_selected("ARMCD", "ARMCD", fixed = TRUE)
      )
    )
  )
  ```
  :::
