---
title: "Exercise 1"
---

Create your first `teal` application!

Reference:

- [`teal::init()`](https://insightsengineering.github.io/teal/latest-tag/reference/init.html) - the main function to create the application
- [`teal.data::teal_data()`](https://insightsengineering.github.io/teal.data/latest-tag/reference/teal_data.html) - data input for teal application
- [`teal::example_module()`](https://insightsengineering.github.io/teal/latest-tag/reference/example_module.html) - a dummy module

### Example

Using `iris` and `mtcars` datasets.

```{r ex, message = FALSE}
# load teal and all dependent packages
library(teal)

# create empty `teal_data` object
data <- teal_data()

# execute code within it
data <- within(data, {
  IRIS <- iris
  MTCARS <- mtcars
})

app <- init(
  data = data,
  modules = list(
    example_module()
  )
)

if (Sys.getenv("QUARTO_ROOT") == "") {
  shinyApp(app$ui, app$server)
}
```

```{r save_script, include = FALSE}
code <- paste0(knitr::knit_code$get("ex"), collapse = "\n")
writeLines(code, "scripts/exercise_1.R")
```

```{r parse_shinylive_url, include = FALSE}
url <- roxy.shinylive::create_shinylive_url(code)
```

### App

```{r shinylive_iframe, echo = FALSE, out.width = '150%', out.extra = 'style = "position: relative; z-index:1"', purl = FALSE}
knitr::include_url(url, height = "800px")
```

### Exercise

```{r shinylive_link, echo = FALSE, results = 'asis', purl = FALSE}
cat(sprintf("[Open editor in Shinylive](%s)\n\n", url))
```

Change the code above to use ADAM datasets. Please use following dataset(s):

- `teal.data::rADSL` - a dummy ADSL dataset
- `teal.data::rADAE` - a dummy ADAE dataset
- `teal.data::rADTTE` - a dummy ADTTE dataset

Please note these are case-sensitive and all are objects (i.e. no functions - no `()` needed).

### Exercise (bonus)

Please read on `teal::modify_title()`, `teal::modify_header()`, `teal::modify_footer()` [here](https://insightsengineering.github.io/teal/latest-tag/reference/teal_modifiers.html) to further customise your application.
