---
title: "Exercise 5"
---

Use transform module to customize outputs from modules.

Reference:

- ["Transform Module Output"](https://insightsengineering.github.io/teal/latest-tag/articles/transform-module-output.html) - article describing the functionality

### Code

Consider a following custom module:

```{r ex-module, message = FALSE}
library(teal)
library(teal.widgets) # optional extension for UI convinience functions
library(teal.reporter)
library(dplyr)
library(ggplot2)

my_custom_module_ui <- function(id, decorators) {
  ns <- NS(id)

  standard_layout(
    output = div(fluidRow(column(
      width = 12,
      br(), hr(),
      plotOutput(ns("plot"))
    ))),
    encoding = div(
      simple_reporter_ui(ns("simple_reporter")),
      br(),
      tags$label('Encodings', class = 'text-primary'),
      helpText('Analysis Data:', tags$code('ADSL')),
      selectInput(
        inputId = ns("variable"),
        label = "Select variable",
        choices = NULL
      ),
      # render decorators input (if any)
      hr(),
      ui_transform_teal_data(ns("decorate"), transformators = decorators),
      hr(),
      actionButton(
        inputId = ns("src"),
        label = "Show R code",
        width = "100%"
      )
    )
  )
}

my_custom_module_srv <- function(id, data, reporter, filter_panel_api, decorators) {
  moduleServer(id, function(input, output, session) {

    updateSelectInput(
      inputId = "variable",
      choices = data()[["ADSL"]] |> select(where(is.numeric)) |> names()
    )

    # add plot call to qenv
    result <- reactive({
      req(input$variable)
      within(
        data(),
        {
          my_plot <- ggplot(ADSL, aes(x = input_var)) +
            geom_histogram()
          my_plot
        },
        input_var = as.name(input$variable)
      )
    })

    # apply decorator
    result_decorated <- srv_transform_teal_data(
      "decorate",
      data = result,
      transformators = decorators
    )

    # render to output the object from qenv
    output$plot <- renderPlot({
      result_decorated()[["my_plot"]]
    })

    # reproducibility
    observeEvent(input$src, {
      showModal(
        ui = modalDialog(
          title = "Reproducible R code",
          tags$pre(
            get_code(result_decorated())
          )
        ),
        session = session
      )
    })

    # reporter
    simple_reporter_srv(
      "simple_reporter",
      reporter = reporter,
      card_fun = function(card = TealReportCard$new(), comment) {
        card$set_name("Histogram Plot")
        card$append_plot(result()[["my_plot"]])
        card$append_fs(filter_panel_api$get_filter_state())
        card$append_encodings(list(param = input$variable))
        if (!comment == "") {
          card$append_text("Comment", "header3")
          card$append_text(comment)
        }
        card$append_src(get_code(result()))
        card
      }
    )

  })
}

my_custom_module <- function(label, decorators = list()) {
  module(
    label = label,
    ui = my_custom_module_ui,
    server = my_custom_module_srv,
    ui_args = list(decorators = decorators),
    server_args = list(decorators = decorators)
  )
}
```

Static (no inputs) decorator:
```{r ex-dec-static}
static_decorator <- teal_transform_module(
  label = "Static decorator",
  server = function(id, data) {
    moduleServer(id, function(input, output, session) {
      reactive({
        req(data())
        within(data(), {
          my_plot <- my_plot +
            ggtitle("This is a better title")
        })
      })
    })
  }
)
```

Interactive decorator:
```{r ex-dec-interactive}
interactive_decorator <- teal_transform_module(
  label = "Interactive decorator",
  ui = function(id) {
    ns <- NS(id)
    div(
      textInput(ns("plot_title"), "Plot title", value = "Awesome title")
    )
  },
  server = function(id, data) {
    moduleServer(id, function(input, output, session) {
      reactive({
        req(data())
        within(data(),
          {
            my_plot <- my_plot +
              ggtitle(my_title)
            my_plot
          },
          my_title = input$plot_title
        )
      })
    })
  }
)
```

Application:

```{r ex-app, message = FALSE}
data <- teal_data()
data <- within(data, {
  ADSL <- rADSL
})

app <- init(
  data = data,
  modules = list(
    my_custom_module("no decorators"),
    my_custom_module("static decorator", decorators = static_decorator),
    my_custom_module("interactive decorator", decorators = interactive_decorator)
  )
)

if (Sys.getenv("QUARTO_ROOT") == "") {
  shinyApp(app$ui, app$server)
}
```

```{r save_script_1, include = FALSE}
code <- paste0(c(
  knitr::knit_code$get("ex-module"),
  knitr::knit_code$get("ex-dec-static"),
  knitr::knit_code$get("ex-dec-interactive"),
  knitr::knit_code$get("ex-app")
), collapse = "\n")
writeLines(code, "scripts/exercise_5_1.R")
```

```{r parse_shinylive_url_1, include = FALSE}
url <- roxy.shinylive::create_shinylive_url(code)
url_editor <- roxy.shinylive::create_shinylive_url(code, mode = "editor")
```

### App

```{r shinylive_iframe_1, echo = FALSE, out.width = '150%', out.extra = 'style = "position: relative; z-index:1"', purl = FALSE}
knitr::include_url(url, height = "800px")
```

### Exercise

Create a decorator for the following application using `teal.modules.general::tm_g_scatterplot()`.

Please note that the final object name is `plot` - see the documentation [here](https://insightsengineering.github.io/teal.modules.general/latest-tag/reference/tm_g_scatterplot.html#decorating-module).

```{r ex, message = FALSE}
library(teal.modules.general)
data <- teal_data() |> within(ADSL <- rADSL)

app <- init(
  data = data,
  modules = list(
    tm_g_scatterplot(
      x = data_extract_spec(
        dataname = "ADSL",
        select = select_spec(
          label = "Select variable:",
          choices = variable_choices(data[["ADSL"]], "AGE"),
          selected = "AGE"
        )
      ),
      y = data_extract_spec(
        dataname = "ADSL",
        select = select_spec(
          label = "Select variable:",
          choices = variable_choices(data[["ADSL"]], "BMRKR1"),
          selected = "BMRKR1"
        )
      ),
      # Modify here!
      decorators = list()
    )
  )
)

if (Sys.getenv("QUARTO_ROOT") == "") {
  shinyApp(app$ui, app$server)
}
```

```{r save_script_2, include = FALSE}
code <- paste0(c(
  knitr::knit_code$get("ex")
), collapse = "\n")
writeLines(code, "scripts/exercise_5_2.R")
```

```{r parse_shinylive_url_2, include = FALSE}
url <- roxy.shinylive::create_shinylive_url(code)
url_editor <- roxy.shinylive::create_shinylive_url(code, mode = "editor")
```

```{r shinylive_link, echo = FALSE, results = 'asis', purl = FALSE}
cat(sprintf("[Open editor in Shinylive](%s)\n\n", url_editor))
```

::: {.callout-tip collapse="true"}
## Answer

```{r, eval = FALSE}
decorators = list(
  plot = teal_transform_module(
    label = "Custom decorations",
    ui = function(id) {
      ns <- NS(id)
      div(
        textInput(ns("plot_title"), "Plot title", value = "Awesome title")
      )
    },
    server = function(id, data) {
      moduleServer(id, function(input, output, session) {
        reactive({
          req(data())
          within(data(),
            {
              plot <- plot +
                ggtitle(my_title)
              plot
            },
            my_title = input$plot_title
          )
        })
      })
    }
  )
)
```
:::
